---
title: "acs_data_pull"
output: html_document
---

```{r setup, include=FALSE}
install.packages("tidyverse", "tidycensus")
library(tidyverse)
library(tidycensus)

census_api_key("4ce84da33024270337d2c7a57c4b2cbf6bc78f6c")
```

```{r}
#Pulling 2017-2013 Data

census_2017 <- get_acs(
  geography = "zip code tabulation area", 
  survey = "acs5",
  geometry = FALSE,
  year = 2017,
  output = "wide",
  variables = c( pop_17 = "B01003_001E",
    pov_pct_17 = "C17002_001E", # poverty rate
    hh_inc_med_17 = "B25119_001E", # hh_inc_med
    rent_gross_med_17 = "B25064_001E", # rent_gross_med
    pop_race_asian_num_17 = "B03002_006E", # pop_race_asian_num
    pop_race_black_num_17 = "B03002_004E", # pop_race_black_num
    pop_race_hisp_num_17 = "B03002_012E", # pop_race_hisp_num
    pop_race_white_num_17 = "B03002_003E", # pop_race_white_num
    total_units_rent_17 = "B25032_013E", # 	total_units_rent
    total_units_17 = "B25024_001E")) %>%
      mutate(
    pop_race_asian_prc_17 = (pop_race_asian_num_17/pop_17)*100,
    pop_race_black_prc_17 = (pop_race_black_num_17/pop_17)*100,
    pop_race_hisp_prc_17 = (pop_race_hisp_num_17/pop_17)*100,
    pop_race_white_prc_17 = (pop_race_white_num_17/pop_17)*100)
# %>%
#   select("NAME", "variable", "estimate") 
# %>%
#   pivot_wider(id_cols = c("variable"), names_from = "NAME", values_from = "estimate")
# census_2017 <- census_2017

  # group_by(NAME) %>%
  # mutate(
  #   pop_race_asian_prc_17 = (pop_race_asian_num_17/pop_17),
  #   pop_race_black_prc_17 = (pop_race_black_num_17/pop_17),
  #   pop_race_hisp_prc_17 = (pop_race_hisp_num_17/pop_17),
  #   pop_race_white_prc_17 = (pop_race_white_num_17/pop_17) 
```
```{r}
#Pulling 2012-20 Data
census_2012 <- get_acs(
  geography = "zip code tabulation area", 
  survey = "acs5",
  geometry = FALSE,
  output = "wide",
  year = 2012,
  variables = c( 
    pop_12 = "B01003_001E",
    pov_pct_12 = "C17002_001E", # poverty rate
    hh_inc_med_12 = "B25119_001E", # hh_inc_med
    rent_gross_med_12 = "B25064_001E", # rent_gross_med
    pop_race_asian_num_12 = "B03002_006E", # pop_race_asian_num
    pop_race_black_num_12 = "B03002_004E", # pop_race_black_num
    pop_race_hisp_num_12 = "B03002_012E", # pop_race_hisp_num
    pop_race_white_num_12 = "B03002_003E", # pop_race_white_num
    total_units_rent_12 = "B25032_013E", # 	total_units_rent
    total_units_12 = "B25024_001E" # total_units
    )
    ) %>%
  mutate(
    pop_race_asian_prc_12 = (pop_race_asian_num_12/pop_12)*100,
    pop_race_black_prc_12 = (pop_race_black_num_12/pop_12)*100,
    pop_race_hisp_prc_12 = (pop_race_hisp_num_12/pop_12)*100,
    pop_race_white_prc_12 = (pop_race_white_num_12/pop_12)*100
  )


# %>%
#   select("NAME", "variable", "estimate") %>%
#   pivot_wider(id_cols = c("variable"), names_from = "NAME", values_from = "estimate") 
# %>%
#   mutate(
#     pop_race_asian_prc_12 = pop_race_asian_num_12/pop_12,
#     pop_race_black_prc_12 = pop_race_black_num_12/pop_12,
#     pop_race_hisp_prc_12 = pop_race_hisp_num_12/pop_12,
#     pop_race_white_prc_12 = pop_race_white_num_12/pop_12
#   )

```

## Binding Rows
```{r}
census_join <- census_2017 %>%
  left_join(census_2012, by = c("NAME", "GEOID")) %>%
  select(
    NAME,
    GEOID,
    pop_17 = pop_17,
    pov_pct_17 = pov_pct_17, # poverty rate
    hh_inc_med_17 = hh_inc_med_17, # hh_inc_med
    rent_gross_med_17 = rent_gross_med_17, # rent_gross_med
    pop_race_asian_num_17 = pop_race_asian_num_17, # pop_race_asian_num
    pop_race_black_num_17 = pop_race_black_num_17, # pop_race_black_num
    pop_race_hisp_num_17 = pop_race_hisp_num_17, # pop_race_hisp_num
    pop_race_white_num_17 = pop_race_white_num_17, # pop_race_white_num
    total_units_rent_17 = total_units_rent_17, # 	total_units_rent
    total_units_17 = total_units_17,
    pop_race_asian_prc_17 = pop_race_asian_prc_17,
    pop_race_asian_prc_17 = pop_race_asian_prc_17,
    pop_race_hisp_prc_17 = pop_race_hisp_prc_17,
    pop_race_white_prc_17 = pop_race_white_prc_17,
    pop_12,
    pov_pct_12,
    hh_inc_med_12,
    rent_gross_med_12,
    pop_race_asian_num_12,
    pop_race_black_num_12,
    pop_race_hisp_num_12,
    pop_race_white_num_12,
    total_units_rent_12,
    total_units_12
  ) %>%
  mutate(pop_prc_ch = (pop_17 - pop_12)/pop_17,
         pov_pct_ch = (pov_pct_17 - pov_pct_12)/pov_pct_17,
         hh_inc_med_ch = (hh_inc_med_17 - hh_inc_med_12)/hh_inc_med_17,
         rent_gross_med_ch = (rent_gross_med_17 - rent_gross_med_12)/rent_gross_med_17,
         total_units_rent_ch = (total_units_rent_17 - total_units_rent_12)/total_units_rent_17,
         )
```
# Joining with eviction data
```{r}
str_remove(census_join, "[ZCTA5 ]")
eviction <- read_csv("eviction_zcta_17to19.csv")

eviction_acs_ <- eviction %>%
  left_join(census_join, by = )
```

    

#census <- rbind(census_2017, census_2012) 

# %>%
#   mutate(pop_prc_ch = (pop_17 - pop_12)/pop_17,
#          pov_pct_ch = (pov_pct_17 - pov_pct_12)/pov_pct_17,
#          hh_inc_med_ch = (hh_inc_med_17 - hh_inc_med_12)/hh_inc_med_17,
#          rent_gross_med_ch = (rent_gross_med_17 - rent_gross_med_12)/rent_gross_med_17,
#          total_units_rent_ch = (total_units_rent_17 - total_units_rent_12)/total_units_rent_17,
#          )
```

## Notes

```{r}
  # select(
  #   "pov_pct" = "C17002_001", # poverty rate
  #   "hh_inc_med" = "B25119_001E", # hh_inc_med
  #   "rent_gross_med" = "B25064_001E", # rent_gross_med
  #   #acs_vars("B25070_{7:10*}E") # rent_burden_num
  #   "pop_race_asian_num" = "B03002_006E", # pop_race_asian_num
  #   "pop_race_black_num" = "B03002_004E", # pop_race_black_num
  #   "pop_race_hisp_num" = "B03002_012E", # pop_race_hisp_num
  #   "pop_race_white_num" = "B03002_003E", # pop_race_white_num
  #   "total_units_rent" = "B25032_013E", # 	total_units_rent
  #   "total_units" = "B25024_001E" # total_units
  #   )
  #   )
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
